---
title: "Model Selection"
author: "Aziz Mohammed"
date: "September 19, 2018"
output: ioslides_presentation
---

## Choosing Best Predictors

### model selection is difficult for
- multivariable
- generalized regression model

### In this project, a simple case is considered
- single variable and 
- linear regression model

### mtcars dataset is used
- mpg as outcome variable 
- the remaing 10 variables are predictors

## How to Select the Best Predictor?

### ui.R in shiny inputs the number of predictors desired
- min = 2, max = 11
- error is generated if input is out of range

### server.R in shiny executes the best predictor selection
- fits mpg vs. each predictor
- computes pvalue for each predictor
- predictor with least pvalue is selected

### project outputs
- plot of best predictor vs mpg
- name and pvalue of predictor

## R Code for Fitting the Best Predictor 

```{r cars, echo = TRUE, comment=""}
data(mtcars)
fit <- lm(mtcars$mpg ~ mtcars$wt)
summary(fit)$coefficients
```

## R Code for Plotting Best Predictor 

```{r graph, echo=FALSE}
plot(mtcars$wt, mtcars$mpg, xlab = "weight", ylab = "Milesper Gallon",
     cex = 1.5, pch= 16)
abline(fit, col = "blue", lwd = 2)
```

